%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
        %---------------------------------------------------------
    \cventry
    {Senior Software Quality Manager} % Job title
    {QIM Info/ Private Banking} % Organization
    {Lausanne, Switzerland} % Location
    {December 2017 - } % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Try and Hire mission to secure on the-long term, the position of Senior Software Quality manager in a Private Bank of the Vaud canton.}		
            \item {Main mission is a \textbf{global Software Suality assessment }of the software delivered in-shore, near-shore of the Bank (> 70 developers). Maintainer of the SonarQube and quality tool platform for the bank}		
            \item {\textbf{Promotion of DevOps practices}, Software quality and cleancode}	
            \item {Initiator of a \textbf{techlead community }inside the Bank}
            \item {\textbf{Invested in the modernization of the SDLC} to integrate a better control of the quality using tools and dedicated reports.}
        \end{cvitems}
    }
    %---------------------------------------------------------
    \cventry
    {Solution Architect, Tech Lead} % Job title
    {SERIAL SA} % Organization
    {Geneva, Switzerland} % Location
    {Janvier 2017 - Novembre 2017} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {\textit{SERIAL SA is a famous company of 30 years old in Switzerland, delivering IT services. Its activities are focused on Web, ECM, Mobile, BI, Security, and Software Engineering expert skills.}}
            \item { \textbf{1st Trimester 2017 - GHI}: \textbf{Software Audit Quality Assessment and Performance diagnostic} \newline Java, AngularJS, JHipster, Gatling, JMeter, SonarQube, Maven, Bamboo}
            \item { \textbf{2nd Trimester 2017 - GSK Novartis}: \textbf{JEE Tech Lead} \newline Technical review of the project, technical migration and Java expertise\newline Docker, Jenkins, Oracle, Java, Javascript, JSP, W4 Business Engine, Tomcat, Apache, Gradle, JIRA, Bamboo}	
            \item { \textbf{TechTalk}: \textbf{Speaker} \newline Why developers should care about quality ?}		
            \item { \textbf{HSBC Private Banking}: \textbf{Technical lead} \newline member of the Middleware team  \textbf{delivery assessment}, technical expertise and review, international environment and offshore teams\newline Spring / Javascript / Ansible / Maven / Apache Camel / SOA / REST}		
        \end{cvitems}
    }
    
    %---------------------------------------------------------
    \cventry
    {Stakeholder and CTO TOCEA} % Job title
    {METRIXWARE/TOCEA} % Organization
    {Rennes, Nanterre} % Location
    {Jun. 2014 - Dec. 2016} % Date(s)
    {
        \begin{itemize}
            \item {\textbf{2013-2016 } - \textbf{Software Editor : DevOps Dashboarding Solution} Solution to produce KPIs and alerts for DevOps teams by extracting the data of their Software Factory and ALM Solution. Solution initially designed for the SoftAtHome company. \newline \textit{Gradle, Spring, Spring Cloud, Jenkins, Puppet, Foreman, Nexus, Spring MVC, Java, Groovy, JUnit, Spock, Elasticsearch, MySQL, Quartz, GWT,Wicket, JQuery, Mybatis}}
            \item {\textbf{2015-2016 } - \textbf{Software Editor : Komea Software Factory solution} Solution to produce on-demand Software Factories in cloud environment by specifying the team needs. This solution was fully integrated with the other DevOps Dashboarding solution. Main benefit of that solution is to automate the common tasks of integrator and Software Factory maintainers\newline \textit{Jenkins, Redmine, Jira, Salesforce, Puppet, Foreman, SonarQube, Kiuwan, GIT, Nexus, Artifactory, Spring, Spring Cloud}}
            \item \textbf{Semester 2016} - {\textbf{\textbf{Automated Refactoring/Migration} of a Financial Editor product} : \textbf{Fircosoft} Automated migration with Metrixware Refactoring framework of the Fircosoft main product Continuity to a new technological stack. }
            \subitem{\textbf{Test Automation} : refactoring of the customer's product to ease the work of the QA Team by capturing traces and replaying them. Development of a automation test framework.}
            \subitem{\textbf{DevOps} : creation of the build/packaging for the product}
            \subitem{ \textbf{Software Assessment} : Software assessment (code quality, metrics, technologies, tests, architecture) to define a technological roadmap for the customer's product}
            \subitem{\textbf{Technologies} : \textit{SonarQube, Kiuwan, Jacoco, Java, Spring, Spring MVC, XML, Maven, Selenium, JUnit, Mockito, RhinoJS, Javascript, Thymeleaf, JSP, GIT, Groovy}}
            \item { \textbf{2014-2016 } - \textbf{Senior Software Quality Auditor : Adminext/BearingPoint partnership } Main auditor for Software Quality assessments of public french administration and ministry}
            \subitem{ \textbf{Functional audit} : As an auditor, I had to review the quality of the documentation, specifications, the precision of the software implementation based on the requirements of the customer. }
            \subitem{ \textbf{Database/Scheme audit} : As an auditor, I had to review the quality of the database schema of different critical solutions according various best practices, 1-NF, 2-NF, 3-NF, data quality...}
            \subitem{ \textbf{Test Automation} : As an auditor, I had to review the quality of tests and the usage of the different metholodogies TDD, BDD and the maintainability of the automated tests as well producing roadmap to increase the test coverage}
            \subitem{ \textbf{Code quality} : As an SQA Expert, I had to select the appropriate tools to perform Code quality measures and technical debt diagnostic of the customer's software, tune them and their quality profiles. Part of my work is to segregate the results to prioritize and classify the issues according different qualimetry models as Sqale, ISO-9126...}
            \subitem{ \textbf{Continuous Delivery} : As a DevOps coach, I was performing assessments of the build and the whole toolchain to build the customer's solutions basing my approach on methologies such like the Continuous Delivery book, Twelve Factors approach...}
        \end{itemize}
    }
    
    %---------------------------------------------------------
    
    
    %---------------------------------------------------------
    \cventry
    {Cofounder and CTO TOCEA/Echoes Labs} % Job title
    {TOCEA} % Organization
    {Rennes, Quebec} % Location
    {Mar. 2011 - Jun. 2014} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {\textit{Tocea is a innovating company that provides refactoring source-to-source solutions to help the sofware editors to refurbish their legacy sofwares in record time and budget}}
            \item {\textbf{Architect}, main developer of a editor solution of Code Quality analysis, competitor of SonarQube : solution }
            \item {\textbf{Contributor to SonarQube ecosystem} : development of a Saas solution for SonarQube to provide worldwide Quality benchmarks}
            \item{\textbf{DevOps Coach} for SoftAtHome, 60 Developers, 20 QA, \textbf{2012-2014}}		
            \subitem{\textbf{Modernization of S@H Software Factory and build} : C/C++, Jenkins, CMake, Make, SonarQube, Coverity, Bugzilla, HP QC}
            \subitem{\textbf{Test Automation advisor}, and Requirements analysis : Testlink, CPPUnit}
        \end{cvitems}
    }
    
    %---------------------------------------------------------
    \cventry
    {Research Engineer for SERENITEC(SEcurity, REfactoriNg, Internet, TEchnologies) Research Project} % Job title
    {INRIA/IRISA} % Organization
    {Rennes} % Location
    {Septembre. 2007 - Sep. 2010} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {\textbf{Main developer} of a new technology for the detection of \textbf{quality}, reliability and \textbf{security} problems in Web Applications}
            \item {Technical Lead of a research team (2 Phd, 2 Engineers)}
            \item {Code Qualimetry tool development : C/C++, Java}
        \end{cvitems} 
    }
    
    
    %---------------------------------------------------------
\end{cventries}
